---
title: "Indicator - Predators in Norwegian Forests"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    
knit: (function(input_file, encoding) {
  out_dir <- 'pdfOutput';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'PredatorsinNorwegianForests.pdf'))})
---


```{r setup, include=FALSE, message=FALSE}
library(knitr)
library(dplyr)
library(raster)
library(rgdal)
library(tmap)
library(sf)
library(NIcalc)
knitr::opts_chunk$set(echo = TRUE)
```

# Description
This metric reflects the population sizes (in terms of metabolic biomass) of the main large mammalian predators in Norwegian forests: wolves, bears, bold eagle, and lynx.


ECT-klasse | Geographic extant | Ecosystem  | Time series | Last year
---------- | -------------     | ---------- | ------------| ----------
B1         |  Norway           | Forest     | Yes         | 2019


Characteristic |
---------------|
Trophic interactions between large mammalian predators and herbivores|
 


# Wolf

Private username and password
```{r}
myUser <- "anders.kolstad@nina.no"
myPwd  <- "" 
```


Import data from the Norwegian Nature Index.
```{r import, eval=F}
ulv <- NIcalc::importDatasetApi(
  username = myUser,
  password = myPwd,
  indic = "Ulv",
  year = c(1990,2000,2010,2014,2019))
```


Specify the entire land area of Norway as NIunits:
```{r}
myNIunits <- c(allArea = T, parts = T, counties = F)
```

Include all BSunits (municipalities)
```{r}
myPartOfTotal <- 0
```

Storing temp file to save time
```{r, eval=FALSE}
ulv_assemeble <- NIcalc::assembleNiObject(
  inputData = ulv,
  predefNIunits = myNIunits, 
  partOfTotal = myPartOfTotal, 
  indexType = "thematic",
  part = "ecosystem",
  total = "terrestrial")  
saveRDS(ulv_assemeble, "cache/ulv_assemble.rds")
```

```{r}
ulv_assemeble <- readRDS("cache/ulv_assemble.rds")
```



# Map values to polygons
To make these spatially explicit we need the map of the data regions.

Importing data regions
```{r}
rovviltregioner <- sf::st_read("../../data/supportingData/rovviltregioner/rovviltregioner.shp")
```


```{r}
tm_shape(rovviltregioner)+
  tm_polygons(col = "region",
              palette = "RdYlGn")
```

```{r}
#crs(rovviltregioner)
```
The variable values are added to their respective polygons, with one column per year. 
The syntax is standardised, with variable value starting with a `v_` and ending with a four digit year.
```{r}
rovviltregioner$v_2019 <- 
  ulv_assemeble$indicatorValues$'2019'$expectedValue[
     match(rovviltregioner$region, ulv_assemeble$indicatorValues$'2019'$ICunitName)]

rovviltregioner$v_2014 <- 
  ulv_assemeble$indicatorValues$'2014'$expectedValue[
     match(rovviltregioner$region, ulv_assemeble$indicatorValues$'2014'$ICunitName)]

rovviltregioner$v_2010 <- 
  ulv_assemeble$indicatorValues$'2010'$expectedValue[
     match(rovviltregioner$region, ulv_assemeble$indicatorValues$'2010'$ICunitName)]

rovviltregioner$v_2000 <- 
  ulv_assemeble$indicatorValues$'2000'$expectedValue[
     match(rovviltregioner$region, ulv_assemeble$indicatorValues$'2000'$ICunitName)]

rovviltregioner$v_1990 <- 
  ulv_assemeble$indicatorValues$'1990'$expectedValue[
     match(rovviltregioner$region, ulv_assemeble$indicatorValues$'1990'$ICunitName)]
```


The reference values are based on expert opinion, and is constant for all years. The workflow only supports a single reference value, so we don't need to specify a year.
```{r}
rovviltregioner$reference <- 
  ulv_assemeble$referenceValues$expectedValue[
     match(rovviltregioner$region, ulv_assemeble$referenceValues$ICunitName)]
```


Rename
```{r}
predator_var <- rovviltregioner
```


```{r}

values <- tm_shape(predator_var)+
  tm_polygons(
    title = "Wolves - 2019",
    col = "v_2019",
    palette = "RdYlGn",
    breaks = c(0, 10, 20, 30, 40, 50, 60))

values2 <- tm_shape(predator_var)+
  tm_polygons(
    title = "Wolves - 2010",
    col = "v_2010",
    palette = "RdYlGn",
    breaks = c(0, 10, 20, 30, 40, 50, 60))

refs <- tm_shape(predator_var)+
  tm_polygons(
    title = "Wolves - reference",
    col = "reference")

tmap_arrange(values, values2, refs)
```


# Export
We will keep the original shape format for as long as possible, but this will later become rasterized.

```{r, eval=F}
sf::st_write(predator_var, "../../data/variables/forestPredators.shp")
```

