---
title: "Indicator - NameOfIndicator"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    
knit: (function(input_file, encoding) {
  out_dir <- 'pdfOutput';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'nameOfIndicator.pdf'))})
---


```{r setup, include=FALSE, message=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

# Description
*Add a description about the metric/indicator and fill in the table below*.


ECT-klasse | Geographic extant | Ecosystem   | Time series | Last year
---------- | -------------     | ----------  | ------------| ----------
?? e.g. A2 |  e.g Norway       | e.g. Forest | Yes/No      | e.g. 2022



You can use the headers suggetsed below, and costumise as needed.

# Data prepartion


# Reference values

# Map values to polygons


# Export
Export the maps with the variables to `data/variables/MyFile`. You should not rasterize shape files at this stage. If the data is in the shape format, you should export it using `sf::st_write()` with one column names `value`, and one column names `reference`. If you have a time series, you need one file per year and the year should come at the end of the file naem(all esle remeining the same).  If you have a raster, add the vallues to band 1, and the referecne value to band 2.   
```{r, eval=F}
#sf::st_write(..., "../../data/variables/....shp")
```

