---
title: "Targets test"
output: pdf_document
---
# Testing the targets workflow

```{r}
source("functions.R")
```

```{r, message=F, warning=F}
pkg <- c("dplyr",
          "tmap",
          "sf",
          "webshot",
          "terra",
          "raster",
          "stringr"
          )
lapply(pkg, require, character.only = TRUE)
```


# File / Variables
```{r}
v_fp_file <- "../data/variables/forestPredators.shp"
```

# Rescale
```{r}

data <- v_fp_file

# load file
data_i <- sf::st_read(data)
head(data_i)  
  
```
Get the column names that start with "v_" (these are the variable estimates)
```{r}
cols <- names(data_i)[str_detect(names(data_i), "v_")]
cols
```
Get the associated column numbers
```{r}
cols_num <- which(names(data_i) %in% cols)
cols_num
```
For each column identified above, divide the values with the reference value.
The column with reference values is always names 'reference'.
The warning is OK. It's just that data_i[,i] also include a 'geometry' column. 
```{r}
for(i in cols_num){
    print(i)
    data_i[,i] <- data_i[,i]/data_i[,"reference"]
}
head(data_i)
```
See how Rovviltregion 4 in 2019 had the value 20.3, and this was rescaled to become 20.3/44 = 0.46.

Raname columns from v_ to i_ to say that they have become rescaled.
```{r}
names(data_i)[str_detect(names(data_i), "v_")] <- 
    str_replace(cols,
                "v_", "i_")
```

Remove the reference value.
```{r}
  data_i <- data_i %>% 
    dplyr::select(-reference)
  head(data_i)
```

# Process

This target takes the indicator name and crops it to the extent of Viken
county. It then rasterizes the data if it is not already, using the master grid as a
template. Finally, it masks the raster based on the ecosystem delineation to remove
pixels that do not correspond to the ecosystem that this indicator is designed for.

```{r}
county_file <- "R:/GeoSpatialData/AdministrativeUnits/Norway_AdministrativeUnits/Converted/Norway_County/Fylke_polygon_2020.shp"

masterGrid_50_file <- "../data/supportingData/masterGrid50m.tif"

ecoMap_file <- "../data/supportingData/ecomap_viken.tif"

```

```{r}
counties <- sf::st_read(county_file)
masterGrid_50 <- terra::rast(masterGrid_50_file)
ecoMap <- terra::rast(ecoMap_file)

indicator <- data_i
```


Subset the counties data to only include the geometry for Viken
```{r}
viken <- counties[counties$NAVN=="Viken",]
```

Crop to the extent of the master gird (essentially the extent of viken)
```{r}
indicator_c <- sf::st_crop(indicator, terra::ext(masterGrid_50))
```
the rasterize function cannot take sf objects, so we have to convert to spatVector
```{r}
i_c_terra <- terra::vect(indicator_c)
```

Get the names of the columns that contain indicator values
```{r}
cols <- names(i_c_terra)[str_detect(names(i_c_terra), "i_")]
cols  
```

Get the corresponding column numbers
```{r}
cols_num <- which(names(i_c_terra) %in% cols)
cols_num
```
make for-loop to create raster brick with one raster layer per year.
```{r}

RS <- rast(masterGrid_50)
for(i in cols){
      print(i)
      out <- terra::rasterize(i_c_terra, masterGrid_50, field=c(i))
      RS <- c(RS, out)
    }
names(RS)
```
This temp file is just for plotting
```{r}
temp <- round(RS[[1]], 2)
```

```{r, warning=F, fig.width= 3, fig.height=2}
#plot(temp, plg=list(title="Indicator value", bty = "o"))
```

Mask raster brick according to ecomap and the chosen ecosystem
```{r}
ecosystem <- "forests"
```

These ecosystem codes should be confirmed
```{r}
ecosystemCode <- ecosystem %>%
  dplyr::recode(
                forests = 101,
                wetlands = 501,
                'open areas' = 401,
                urban = 940,
                agriculture = 931,
                freshwater = 601,
                marine = 701)

```

```{r}
eco <- ecoMap
eco[eco != ecosystemCode] <- NA
```

```{r, fig.width= 3, fig.height=2}
plot(eco)
```

```{r}
tempM2 <- terra::mask(RS, eco)
```

```{r}
plot(tempM2$i_2019)
```





